\documentclass[12pt]{article}
\usepackage{listings}
\usepackage{color}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\definecolor{mygray}{rgb}{0.4,0.4,0.4}
\definecolor{mygreen}{rgb}{0,0.8,0.6}
\definecolor{myorange}{rgb}{1.0,0.4,0}

\lstset{
basicstyle = \ttfamily,columns=fullflexible,
commentstyle=\color{mygray},
frame=single,
numbers=left,
numbersep=5pt,
numberstyle=\tiny\color{mygray},
keywordstyle=\color{mygreen},
showspaces=false,
showstringspaces=false,
stringstyle=\color{myorange},
tabsize=2
}

\pagestyle{empty}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\begin{center}
{\bf lab 02 Makefiles}

\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}
\setlength{\tabcolsep}{6pt} % General space between cols (6pt standard)
\renewcommand{\arraystretch}{.5} % General space between rows (1 standard)

\vskip.15in
\noindent\textbf{Instructions:} In this lab please develop a makefile for the code provided in your lab02 directory.

Please ensure the following:
\begin{enumerate}
\item Rules to compile each .cpp file into a .o file.  Those .o files should be create in an objs directory. 
\begin{itemize}
\item You will need a rule to create a obj directory and then put the .o file in there when compiling.
\end{itemize}
\item Add an ``all'' rule that:
\begin{enumerate}
\item Compiles all cpp files to .o files into the objs directory
\item After creating the .o files, link them into an executable file in the lab02 directory.
\end{enumerate}
\item Create a rule ``run'' that runs your program with valgrind.
\item Finally create a rule ``clean'' that removes the object files, and the executable.
\end{enumerate}

\vskip.15in
\noindent\textbf{Google Help:} \\
For this assignment feel free to Google help.  Just make sure you cite!  I recommend putting a comment in your makefile telling me which website you used.

\vskip.15in
\noindent\textbf{How to turn in:} \\
Turn in via GitHub.  Ensure the file(s) are in your directory and then:
\begin{itemize}
\item \$ git add $<$files$>$
\item \$ git commit 
\item \$ git push
\end{itemize}

\vskip.15in
\noindent\textbf{Due Date:}
September 01, 2020 2359

\vskip.15in
\noindent\textbf{Teamwork:} No teamwork, your work must be your own.

\end{document}
