\documentclass[12pt]{article}
\usepackage{listings}
\usepackage{color}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\definecolor{mygray}{rgb}{0.4,0.4,0.4}
\definecolor{mygreen}{rgb}{0,0.8,0.6}
\definecolor{myorange}{rgb}{1.0,0.4,0}

\lstset{
basicstyle = \ttfamily,columns=fullflexible,
commentstyle=\color{mygray},
frame=single,
numbers=left,
numbersep=5pt,
numberstyle=\tiny\color{mygray},
keywordstyle=\color{mygreen},
showspaces=false,
showstringspaces=false,
stringstyle=\color{myorange},
tabsize=2
}

\pagestyle{empty}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\begin{center}
{\bf lab 12 Basic sorting: Selection and Insertion Sort}

\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}
\setlength{\tabcolsep}{6pt} % General space between cols (6pt standard)
\renewcommand{\arraystretch}{.5} % General space between rows (1 standard)

\vskip.15in
\noindent\textbf{Part 1:} Implement Selection and Insertion sort for your Array List class.  Then implement any of the basic sorts (Bubble, Selection, or Insertion) for a singly Linked List.
\\
 \textbf{Note: Keep your old implementation and append the following functions:}

\begin{lstlisting}[language=C++]{Name=test2}

template <class T>
class Array {
    private:
    /* You fill out the private contents. */

    public:
    /* Runs a bubble sort algorithm on the array.
     * The array shall be ordered from least to greatest
     */
    void bubbleSort();

    /* Runs a selection sort algorithm on the array.
     * The array shall be ordered from least to greatest
     */
    void selectionSort();

    /* Runs a insertion sort algorithm on the array.
     * The array shall be ordered from least to greatest
     */
    void insertionSort();

    /* Runs the sort routing you believe is the best. */
    void sort();

};


/* SLL = Singly Linked List */
template<class T>
class SLList {
    public:
        /* Sort the linked list.  You may use any sort algorithm you wish */
        void sort();
};

\end{lstlisting}

\vskip.15in
\noindent\textbf{Write some test cases:} \\
Create some test cases, using cxxtestgen, that you believe would cover all aspects of your code.

\vskip.15in
\noindent\textbf{Part 2: Performance} \\
Generate a graph to compare the performance of bubble sort, selection sort, insertion sort, and the sort you chose for a Singly Linked List.  Your graph should have data size on the x axis and time on the y axis.  Make sure to label each graph line!  Please turn in as a .pdf!

\vskip.15in
\noindent\textbf{Auto Grader:} \\
The auto grader is only grading part 1, I will have to assess part 2.  In other words, if the auto grade issues a 100, that is only for part 1!

\vskip.15in
\noindent\textbf{Memory Management:} \\
Ensure there are no memory leaks in your code.  Please run Valgrind on your tests to ensure no memory leaks.
\vskip.15in

\vskip.15in
\noindent\textbf{STL:} \\
You may not use the STL.

\vskip.15in
\noindent\textbf{How to turn in:} \\
Turn in via GitHub.  Ensure the file(s) are in your directory and then:
\begin{itemize}
\item \$ git add $<$files$>$
\item \$ git commit 
\item \$ git push
\end{itemize}

\vskip.15in
\noindent\textbf{Due Date:}
October 05, 2020 2359

\vskip.15in
\noindent\textbf{Teamwork:} No teamwork, your work must be your own.

\end{document}
